---
title: "Get Started"
resource_files:
  - '../inst/svelte-app/public/'
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

`svelteR` assumes that the app structure was created
using this [svelte template](https://github.com/sveltejs/template).
In short, you ran this code in a terminal:

```{bash, eval=FALSE}
npx degit sveltejs/template svelte-app
cd svelte-app
npm install
```

Where "svelte-app" is the name of the folder you want to create the app in.
There are two things you need to take care of in your svelte app
to ensure that it works as a standalone app, as well as embedded
into this document.

Modify `index.html` to look like this:

```html
<!DOCTYPE html>
<html lang="en">
<head>
	<meta charset='utf-8'>
	<meta name='viewport' content='width=device-width,initial-scale=1'>
	<title>Svelte app</title>
	<link rel='icon' type='image/png' href='/favicon.png'>
	<link rel='stylesheet' href='/global.css'>
	<link rel='stylesheet' href='/build/bundle.css'>
	<script defer onload="window['svelte-app']('body', {name: 'main test'})" src='/build/bundle.js'></script>
</head>
<body id="body">
</body>
</html>
```

And `src/main.js` like this:

```js
import App from './App.svelte';

const app = (targetId, props) => new App({
	target: document.getElementById(targetId),
	props: props
});

// 'svelte-app' has to be a unique name for your app.
// make sure it is the same as in window['svelte-app'] in index.html
// a good convention is to use the name of your app-directory
window['svelte-app'] = app;
export default app;
```

`app` is now a function of a `targetID` and some properties.
This allows us to include the same app multiple times into
different divs and pass different properties to them.

Then run the following in the app directory to preview the app
on localhost while working:

```{bash, eval=FALSE}
npm run dev
```

And finally build the app
(so that you can ship it or include it in this document):

```{bash, eval=FALSE}
npm run build
```

This will create the necessary files in a folder of your app named
"public/build/", which `svelteR` assumes to exist.

## Demo Time!

Embed the same app multiple times with different properties.
`props` takes and R list which is converted to JSON to be used
in the app.
The path should be relative to you Rmd file.
You can use and example app installed with this package with:

```{r, eval=FALSE}
svelteR::include_svelte(name = "svelte-app",
                        # path relative to your Rmd file
                        path = system.file("svelte-app", package = "svelteR"),
                        props = list(name = "First"))
```

This will embed everything the app needs in the html file.
If you want to avoid this, you can pass `self_contained = FALSE` to
the function.
However, for the purpose of this documentation with pkgdown, we need to reference
the path like this:

```{r}
svelteR::include_svelte(name = "svelte-app",
                        # path relative to your Rmd file
                        path = "../inst/svelte-app",
                        props = list(name = "First"))
```

And include the app as a resource in the yaml header:

```
resource_files:
  - '../inst/svelte-app/public/'
```

And again:

```{r}
svelteR::include_svelte(name = "svelte-app",
                        path = "../inst/svelte-app",
                        props = list(name = "Second"))
```

## CSS Priority

Note that the demo app included in this package
(see `system.file("svelte-app", package = "svelteR")`)
looks slightly different when built on it's own,
in a fresh Rmarkdown document or in this pkgdown documentation
website.
The reason for this is the order in which css files are imported.
I am willing to sell this as a feature instead of a bug.
You can use this to your advantage, if you know the rules.
So here they come:

- Custom css for your Rmarkdown document, under which
  the bootstrap framework of this documentation site made
  with pkgdown falls, will have precedence over
  `global.css` in your `svelte-app/public/` folder.
- css defined in individual components of the svelte app,
  or the main `App.svelte` will have precedence over both.
  

